A Partitioning Algorithm for \\ Maximum Common Subgraph Problems

### 2017-08-15 talk/talk.tex
Muck around

        \node (logo) [anchor=north east, shift={(-0.6cm,-0.6cm)}] at (current page.north east) {
            \includegraphics*[keepaspectratio=true,scale=0.7]{UoG_keyline.pdf}
        };

@@

@@

\begin{frame}[plain,noframenumbering]
    \begin{center}
        \vspace*{4em}
        \url{http://www.dcs.gla.ac.uk/~ciaran} \\
        \vspace{1em}
        \href{mailto:ciaran.mccreesh@gla.ac.uk}{\nolinkurl{ciaran.mccreesh@gla.ac.uk}} \\
    \end{center}

>>>>

        \node (logo) [anchor=north east, shift={(-0.3cm,-0.6cm)}] at (current page.north east) {
            \includegraphics*[keepaspectratio=true,scale=0.65]{UoG_keyline.pdf}
        };

@@

\begin{frame}{The McSplit Algorithm}
    \begin{itemize}
        \item We can use a compact backtrackable data structure which splits vertices into
            partitions
        \item Propagation is just refining partitions
        \item Soft all-different can be calculated by counting rather than matching
    \end{itemize}
\end{frame}

@@

\begin{frame}[plain,noframenumbering]
    \begin{center}
        \vspace*{4em}
        \url{http://www.dcs.gla.ac.uk/~ciaran} \\
        \vspace{1em}
        \href{mailto:ciaran.mccreesh@glasgow.ac.uk}{\nolinkurl{ciaran.mccreesh@glasgow.ac.uk}} \\
    \end{center}
